Team size and composition in home health care

### 2023-10-19 paper-presentation/paper-presentation.qmd
Minor

    # Draw the graph
    pos = nx.spring_layout(G)  # positions for all nodes
    nx.draw_networkx_nodes(G, pos, node_size=700, node_color="skyblue")
    nx.draw_networkx_edges(G, pos, width=1.0, alpha=0.5)
    nx.draw_networkx_labels(G, pos, font_size=20, font_color="white")

>>>>

    # Draw the graph
    pos = nx.spring_layout(G)  # positions for all nodes
    nx.draw_networkx_nodes(G, pos, node_size=700, node_color="tomato")
    nx.draw_networkx_edges(G, pos, width=1.0, alpha=0.5)
    nx.draw_networkx_labels(G, pos, font_size=20, font_color="white")
